```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(dplyr.summarise.inform = FALSE)

library(redcapAPI)
library(dplyr)

# This file contains a list of tokens to access the API of each of the ICARIA HF 
# REDCap project. As these tokens allow to access sensible data, this file is
# not shared. If you need to use this script, you will have to request your API
# tokens through REDCap.
source("tokens.R")

ExportNCAllHealthFacilities <- function(redcap.api.url, redcap.tokens) {
  # Export the non-compliant forms completed in each of the ICARIA Health 
  # Facility REDCap projects and append all data sets in a unique data frame.
  #
  # Args:
  #   redcap.api.url: String representing the URL to access the REDCap API.
  #   redcap.tokens:  List of tokens (Strings) to access each of the ICARIA 
  #                   REDCap projects.
  # 
  # Returns:
  #   Data frame with all the data together of different ICARIA Health 
  #   Facilities.
  
  data <- data.frame()
  for (hf in names(redcap.tokens)) {
    print(paste("Extracting data from", hf))
    
    kREDCapEvents <-("out_of_schedule_arm_1")  
    kREDCapFields <- c("record_id", "comp_contact_type", "comp_child_seen",
                       "comp_why_not_child_seen", "comp_compliant", 
                       "comp_why_not_compliant", "comp_why_phone", 
                       "comp_caretaker_phone", "comp_compliant_2", 
                       "comp_why_not_compliant_2", "comp_date")
    rcon <- redcapConnection(redcap.api.url, redcap.tokens[[hf]])
    hf.data <- exportRecords(
      rcon    = rcon, 
      factors = F, 
      labels  = F, 
      events  = kREDCapEvents,
      fields  = kREDCapFields
    )
    
    hf.data <- cbind(hf = hf, hf.data)
    data <- rbind(data, hf.data)
  }
  
  return(data)
}

# Reporting date
data_timestamp <- Sys.time()

# Retrieve all non-compliant vars of interest of completed forms
non.compliant.data <- ExportNCAllHealthFacilities(kRedcapAPIURL, kRedcapTokens)
non.compliant.data <- non.compliant.data[
  which(non.compliant.data$noncompliant_complete == 2), ]
```

---
title: "ICARIA Non-compliants"
author: "Máximo Ramírez Robles"
date: `r data_timestamp`
output: html_document
---

<style>
body {
  text-align: justify
}
</style>


This script analyses the reasons why the ICARIA participants become 
non-compliant. At the date of this document, a non-compliant participant is a 
participant who didn't come for her last appointment for more than 4 weeks 
considering all EPI visits. To compute that, we use the <i>int_next_visit var
</i> in the Intervention Data Collection Instrument (DCI) (Q24. Return date) of 
the last EPI visit carried out by the participant. The reasons of being 
non-compliant will be retrieved from the Non-compliant DCI.

```{r summary, echo=FALSE}
# Indicator 1: Number of total non-compliant contacts and disaggregated by
# household visits and phone contacts
n.contacts <- nrow(non.compliant.data)
contact.types <- table(non.compliant.data$comp_contact_type)

n.contacts.visit <- contact.types[["1"]]
n.contacts.phone <- contact.types[["2"]]
```

## Summary

A total of <b>`r n.contacts`</b> contacts have been carried out since the 
beginning of the trial (<b>`r n.contacts.visit`</b> household visits and 
<b>`r n.contacts.phone`</b> phone calls).

```{r non.compliant.participants, echo=FALSE}
# We filter the last contact with each non-compliant participant
group.by.participant <- group_by(non.compliant.data, hf, record_id)
last.contacts <- summarise(group.by.participant, comp_date = max(comp_date))
last.contacts <- merge(last.contacts, non.compliant.data)

# Indicator 2: Number of non-compliant participants contacted
n.non.compliant <- nrow(last.contacts)
```

A participant may be contacted more than once. This can happen either because 
the contact was not satisfactory enough to assess the child status or because a 
participant may be non-compliant more than once. Thus, <b>`r n.non.compliant`
</b> participants have been contacted since the beginning of the trial for being 
non-compliant.

### ☖ Household Visits

```{r household.visits, echo=FALSE}
# We filter last contacts done by a household visit
hh.visits <- last.contacts[which(last.contacts$comp_contact_type == 1), ]

# Indicator 3: Number of non-compliant participants who were lastly contacted
#              through a household visit
n.hh.visits <- nrow(hh.visits)

# Indicator 4: Number of non-compliant participants successfully reached by
#              field workers through a household visit (children seen)
seen.participants <- table(hh.visits$comp_child_seen)
n.seen.participants <- seen.participants[["1"]]
n.not.seen.participants <- seen.participants[["0"]]
```

For these <b>`r n.non.compliant`</b> non-compliant participants, 
<b>`r n.hh.visits`</b> were lastly contacted through a household visit: 
<b>`r n.seen.participants`</b> were seen by the ICARIA field workers. The other 
<b>`r n.not.seen.participants`</b> were not seen due to:

```{r hh.why.not.seen, echo=FALSE}
# Indicator 5: Number of non-compliant participants not seen during the last
#              household visit disaggregated by the reason why they were not 
#              seen
hh.visits$comp_why_not_child_seen <- factor(
  x      = hh.visits$comp_why_not_child_seen, 
  levels = 1:4
)
why.not.seen <- table(
  hh.visits$comp_why_not_child_seen[hh.visits$comp_child_seen == 0])

Reason <- c("Absent", "Admitted to hospital", "Dead", "Migrated")
table.why.not.seen <- data.frame(Reason, why.not.seen)
colnames(table.why.not.seen) <- c("Reason", "Code", "n")

knitr::kable(table.why.not.seen[, c("Reason", "n")])
```

For the <b>`r n.seen.participants`</b> that were seen by the ICARIA staff during 
the last household visit, they didn't come to the HF for their last appointment 
due to:

```{r hh.why.not.come.hf, echo=FALSE}
# Indicator 6: Number of non-compliant participants seen during the last
#              household visit disaggregated by the reason why they were not 
#              come to the HF for their last EPI appointment
hh.visits$comp_why_not_compliant <- factor(
  x      = hh.visits$comp_why_not_compliant, 
  levels = c(1:5, 88)  ## 88 = other
)
why.not.come <- table(
  hh.visits$comp_why_not_compliant[
    hh.visits$comp_child_seen == 1 & hh.visits$comp_compliant == 0])

Reason <- c("The child was/is sick", "I forgot", "I do not have the time", 
            "I was away", "I do not want to continue with the study", "Other")
table.why.not.come <- data.frame(Reason, why.not.come)
colnames(table.why.not.come) <- c("Reason", "Code", "n")

knitr::kable(table.why.not.come[, c("Reason", "n")])

table.not.assessed <- table(
  hh.visits$comp_compliant[which(hh.visits$comp_child_seen == 1)], 
  useNA = "always"
)

reported.to.come <- table.not.assessed[2]
absent.caretaker <- table.not.assessed[3]
```

<small><b><u>Note:</u></b> In addition, `r reported.to.come` caretakers reported 
that they came to the HF for the last EPI visit and there are 
`r absent.caretaker` cases in which the caretaker was not around and the ICARIA 
field workers were not able to asses the reason why they didn't come to the HF.
</small>

### ☏ Phone calls

```{r phone.calls, echo=FALSE}
# We filter last contacts done by a phone call
phone.calls <- last.contacts[which(last.contacts$comp_contact_type == 2), ]

# Indicator 7: Number of non-compliant participants who were lastly contacted
#              through a phone call
n.phone.calls <- nrow(phone.calls)

# Indicator 8: Number of caretakers of non-compliant participants successfully 
#              reached by field workers through a phone call
reached.caretakers <- table(phone.calls$comp_caretaker_phone)
n.reached.caretakers <- reached.caretakers[["1"]]
n.not.reached.caretakers <- reached.caretakers[["0"]]
```

On the other hand, <b>`r n.phone.calls`</b> participants were lastly contacted 
through a phone call: <b>`r n.reached.caretakers`</b> were successfully reached. 
For the other <b>`r n.not.reached.caretakers`</b>, the ICARIA field workers were 
not able to speak with the participant's caretaker. In this case, for the
<b>`r n.reached.caretakers`</b> reached caretakers, they reported not coming to
the HF for their last appointment due to:

```{r call.why.not.come.hf, echo=FALSE}
# Indicator 9: Number of non-compliant participants in which their caretakers
#              were reached by phone disaggregated by the reason why they were 
#              not come to the HF for their last EPI appointment
phone.calls$comp_why_not_compliant_2 <- factor(
  x      = phone.calls$comp_why_not_compliant_2, 
  levels = c(1:5, 88)  ## 88 = other
)
why.not.come <- table(
  phone.calls$comp_why_not_compliant_2[
    phone.calls$comp_caretaker_phone == 1 & phone.calls$comp_compliant_2 == 0])

Reason <- c("The child was/is sick", "I forgot", "I do not have the time", 
            "I was away", "I do not want to continue with the study", "Other")
table.why.not.come <- data.frame(Reason, why.not.come)
colnames(table.why.not.come) <- c("Reason", "Code", "n")

knitr::kable(table.why.not.come[, c("Reason", "n")])

table.not.assessed <- table(
  phone.calls$comp_compliant_2[which(phone.calls$comp_caretaker_phone == 1)], 
  useNA = "always"
)

dont.know.if.come <- table.not.assessed[2]
```

<small><b><u>Note:</u></b> In addition, `r dont.know.if.come` caretakers didn't 
know if they had brought their children to the last EPI visit.</small>